Class Exercise: Factors Influencing Abundance & Virus Isolation in Mosquitoes

### 2024-02-02 products/manuscript/Manuscript.qmd
Final push before submission
Updated qmd. removed bib and csl path for now.

---
title: "Class Exercise: Factors Influencing Abundance & Virus Isolation in Mosquitoes"
subtitle: "Which environmental, ecological, and temporal factors impact mosquito populations  "
author: Andrew Ruiz
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../assets/dataanalysis-references.bib
csl: ../assets/apa.csl
editor: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "Class Exercise: Factors Influencing Abundance & Virus Isolation in Mosquitoes"
subtitle: "Which environmental, ecological, and temporal factors impact mosquito populations  "
author: Andrew Ruiz
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
editor: 
  markdown: 
    wrap: 72
---
